---
title: "2017 UCI sockeye commmercial fishery mixed stock analysis"
author: "Andy Barclay"
date: "May 23, 2018"
output: html_document
---

##Set up workspace
###Get functions and load tidy packages
```{r workspace setup, echo=TRUE}

source("C:\\Users\\awbarclay\\Documents\\R\\GitHubCloneFunctions.R")#GCL functions
source("V:\\Analysis\\Staff\\Andy Barclay\\R\\New Functions\\WorkspaceFolders.GCL.R")#A function I wrote

library("tidyverse")

```

###Create output folders 
```{r create folders, echo=TRUE}
#WorkspaceFolders.GCL(Folders=c("Output","rubias"),Subfolders=list(rubias=c("baseline","mixture","output")),wd=getwd())

```

###Create locus control and get genotype data

```{r locus control, echo=TRUE}

#CreateLocusControl.GCL(markersuite = "S138_UCI_24SNPs", username ="awbarclay", password = password)#Locus control

#LOKI2R.GCL(sillyvec="SCIMA17",username="awbarclay",password)#Pull Data from LOKI

#save.image("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/2017 UCIfisheryMixtures/UCI_Sockeye_2017/UCI_Sockeye_2017.Rdata")

load("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/2017 UCIfisheryMixtures/UCI_Sockeye_2017/UCI_Sockeye_2017.Rdata")

loci24 <- LocusControl$locusnames
loci24

```

##Data cleanup
###Check initial sample size
```{r initial sample size, echo=TRUE}

ColSize<-data.frame(row.names = "SCIMA17")
ColSize$Original_N <- SCIMA17.gcl$n
ColSize

```

###Removing individuals with <80% of loci with gentotypes
```{r missloci,echo=TRUE}

MissLOCI=RemoveIndMissLoci.GCL(sillyvec="SCIMA17",proportion=0.8)
MissLOCI

ColSize$AfterMissLoci_N <- SCIMA17.gcl$n
ColSize

```

###Check for duplicate individuals and remove them

```{r dupckeck, echo=TRUE, message=FALSE}

CheckDupWithinSilly.GCL(sillyvec="SCIMA17",loci=loci24,quantile=NULL,minproportion=0.99)

```
```{r remove duplicate fish,results="hide"}

RemoveIDs.GCL(silly="SCIMA17",IDs=6462)#Two duplicates sets identified but remove only one from the set with IDs that are close

```
```{r final sample size}
ColSize$Final_N <- SCIMA17.gcl$n
ColSize

```

###Combine MHCs and mitochondiral markers
```{r combine loci,results="hide"}

 CombineLoci.GCL(sillyvec="SCIMA17",markerset=c("One_MHC2_190","One_MHC2_251"),update=TRUE)
 CombineLoci.GCL(sillyvec="SCIMA17",markerset=c("One_CO1","One_Cytb_17","One_Cytb_26"),update=TRUE)

```

###Create locus list for MSA
```{r final locus vector}

loci<-LocusControl$locusnames
loci

```

##Setup mixtures
###Create vector of mixture names
```{r mixvec, echo=FALSE}

mixvec<-c("Drift17","Drift_Corridor17","West_Kalgin17","Northern_Dist17","ESSN17")

```

###Get mixture IDs from attributes and create mixtures
```{r attributes table}
attr<-as.tibble(SCIMA17.gcl$attributes)
attr

```

####Drift
```{r Drift (district-wide),results="hide",message=FALSE}

Drift17_IDs<-as.character(filter(attr,CAPTURE_LOCATION=="Drift (district-wide)")$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Drift17_IDs),newname="Drift17")

```
```{r Drift (corridor-only),results="hide"}

Drift_Corridor17_IDs<-as.character(filter(attr,CAPTURE_LOCATION=="Drift (expanded corridor-only)")$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Drift_Corridor17_IDs),newname="Drift_Corridor17")

```
####Set gillnet
```{r West/Kalgin Island subdistricts,results="hide"}

West_Kalgin17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("Kalgin Island Subdistrict","Western Subdistrict"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=West_Kalgin17_IDs),newname="West_Kalgin17")

```
```{r Northern District,results="hide"}

Northern_Dist17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("General Subdistrict (north)","General Subdistrict (south)","Eastern Subdistrict"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Northern_Dist17_IDs),newname="Northern_Dist17")

```
```{r Upper Subdistrict (ESSN),results="hide"}

ESSN17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("Cohoe Ninilchik","North K-Beach","South K-Beach","Salamatof"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=ESSN17_IDs),newname="ESSN17")

```
###Check mixture sample sizes
```{r mixture sample sizes,echo=FALSE}

sapply(mixvec,function(mix){get(paste0(mix,".gcl"))$n})

```



