---
title: "2017 UCI sockeye commmercial fishery mixed stock analysis"
author: "Andy Barclay"
date: "May 23, 2018"
output: html_document
---

##Set up workspace
###Get functions and load tidy packages
```{r workspace setup, echo=TRUE}

source("C:\\Users\\awbarclay\\Documents\\R\\GitHubCloneFunctions.R")#GCL functions
source("V:\\Analysis\\Staff\\Andy Barclay\\R\\New Functions\\WorkspaceFolders.GCL.R")#A function I wrote

library("tidyverse")

```

###Create output folders 
```{r create folders, echo=TRUE}
#WorkspaceFolders.GCL(Folders=c("Output","rubias"),Subfolders=list(rubias=c("baseline","mixture","output")),wd=getwd())

```

###Create locus control and get genotype data
```{r locus control, echo=TRUE}

#CreateLocusControl.GCL(markersuite = "S138_UCI_24SNPs", username ="awbarclay", password = password)#Locus control

#LOKI2R.GCL(sillyvec="SCIMA17",username="awbarclay",password)#Pull Data from LOKI

#save.image("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/2017 UCIfisheryMixtures/UCI_Sockeye_2017/UCI_Sockeye_2017.Rdata")

load("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/2017 UCIfisheryMixtures/UCI_Sockeye_2017/UCI_Sockeye_2017.Rdata")
```
###Create initial locus object
The Cook Inlet genetic baseline was analyzed for a 96 SNP locus set.  To reduce analysis cost, the locus set was reduced to 24 loci with the highest FST values
```{r initial locus object}

loci24 <- LocusControl$locusnames
loci24

```

##Data cleanup
###Check initial sample size
```{r initial sample size, echo=TRUE}

ColSize<-data.frame(row.names = "SCIMA17")
ColSize$Original_N <- SCIMA17.gcl$n
ColSize

```

###Removing individuals with <80% of loci with gentotypes
Fish that have gentoypes for less than 80% of loci are likely to have poor quality DNA and might introduce gentotyping errors into the mixture data and reduce the accruacy of the mixed stock analysis (MSA)
```{r missloci,echo=TRUE}

MissLOCI=RemoveIndMissLoci.GCL(sillyvec="SCIMA17",proportion=0.8)
MissLOCI

ColSize$AfterMissLoci_N <- SCIMA17.gcl$n
ColSize

```

###Check for duplicate individuals and remove them
Fish with 99% of gentotype 
```{r dupckeck, echo=TRUE, message=FALSE}

CheckDupWithinSilly.GCL(sillyvec="SCIMA17",loci=loci24,quantile=NULL,minproportion=0.99)

```
```{r remove duplicate fish,results="hide"}

RemoveIDs.GCL(silly="SCIMA17",IDs=6462)#Two duplicates sets identified but remove only one from the set with IDs that are close

```
```{r final sample size}
ColSize$Final_N <- SCIMA17.gcl$n
ColSize

```

###Combine MHCs and mitochondiral markers
These markers are linked and have to be combined into haploid markers in the baseline analysis; therefore, they have to be combined for the the mixed stock analysis
```{r combine loci,results="hide"}

 CombineLoci.GCL(sillyvec="SCIMA17",markerset=c("One_MHC2_190","One_MHC2_251"),update=TRUE)
 CombineLoci.GCL(sillyvec="SCIMA17",markerset=c("One_CO1","One_Cytb_17","One_Cytb_26"),update=TRUE)

```

###Create locus list for MSA
```{r final locus vector}

loci<-LocusControl$locusnames
loci

```

##Setup mixtures
###Create vector of mixture names
```{r mixvec, echo=FALSE}

mixvec<-c("Drift17","Drift_Corridor17","West_Kalgin17","Northern_Dist17","ESSN17")

```

###Get mixture IDs from attributes and create mixture .gcl objects
```{r attributes table}
attr<-as.tibble(SCIMA17.gcl$attributes)
attr

```

####Drift
```{r Drift (district-wide),results="hide",message=FALSE}

Drift17_IDs<-as.character(filter(attr,CAPTURE_LOCATION=="Drift (district-wide)")$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Drift17_IDs),newname="Drift17")

```
```{r Drift (corridor-only),results="hide"}

Drift_Corridor17_IDs<-as.character(filter(attr,CAPTURE_LOCATION=="Drift (expanded corridor-only)")$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Drift_Corridor17_IDs),newname="Drift_Corridor17")

```
####Set gillnet
```{r West/Kalgin Island subdistricts,results="hide"}

West_Kalgin17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("Kalgin Island Subdistrict","Western Subdistrict"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=West_Kalgin17_IDs),newname="West_Kalgin17")

```
```{r Northern District,results="hide"}

Northern_Dist17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("General Subdistrict (north)","General Subdistrict (south)","Eastern Subdistrict"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=Northern_Dist17_IDs),newname="Northern_Dist17")

```
```{r Upper Subdistrict (ESSN),results="hide"}

ESSN17_IDs<-as.character(filter(attr,CAPTURE_LOCATION%in%c("Cohoe Ninilchik","North K-Beach","South K-Beach","Salamatof"))$FK_FISH_ID)
PoolCollections.GCL(collections="SCIMA17",loci=loci,IDs=list(SCIMA17=ESSN17_IDs),newname="ESSN17")

```
###Check mixture sample sizes
```{r mixture sample sizes,echo=FALSE}

sapply(mixvec,function(mix){get(paste0(mix,".gcl"))$n})

```
###Create rubias mixtures
Creating rubias mixture list object and save as .csv files in the default directory - path = "rubias/mixture"
```{r rubias mixtures, results="hide"}

mixtures <- create_rubias_mixture(sillyvec=mixvec,loci=loci)

```

##Set up baseline
Creating a rubias baseline object save as a .csv file in the default directory - path = "rubias/baseline"
To create the baseline object I had to access objects in the [baseline workspace](V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Baseline) 
```{r rubias baseline,results="hide"}

attach("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Baseline/CI2012Baseline.RData")#Attach to Baseline data.

groups <- c("Crescent","West","JCL","SusYen","Fish","KTNE","Kenai","Kasilof")#Reporting groups

groupvec <- groupvec#Same length as the number of baseline pops indicating the reporting group for each pop.

GrCol <- GrCol#Reporting group colors to use for plotting results

baseline <- create_rubias_baseline(sillyvec=PooledNames71,loci=loci,group_names = groups,groupvec = groupvec,baseline_name = "CI71pops24loci")

detach(pos=match(x="file:V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Baseline/CI2012Baseline.RData",table=search()))#Detach from baseline data.

```
##Analyze mixtures in rubias
Analyzing mixture without using the bias correction (method="MCMC") for 25,000 iterations (reps), burning the first 5,000 iterations (burn_in), and thining (sample_int_Pi) by 10 to reduce the size of the results objects.
```{r anlyze mixtures, results="hide"}

run_rubias_mixture(reference=baseline,mixture=mixtures,gen_start_col=5, method = "MCMC", 
                   alle_freq_prior = list(const_scaled = 1), reps = 25000, burn_in = 5000, 
                   pb_iter = 100, sample_int_Pi = 10, pi_prior_pseudo_count_sum = 1, 
                   path = "rubias/output")

```

##Get reporting group results
```{r get results}

repunit_trace<-set_names(lapply(mixvec,function(mix){
  read_csv(paste0("rubias/output/",mix,"_repunit_trace.csv")) %>% 
    mutate(mixture_collection=mix) %>% 
    gather(key="repunit",value="repunit_ppn",Crescent,West,JCL,SusYen,Fish,KTNE,Kenai,Kasilof,-sweep)
  }),mixvec) %>% 
    bind_rows()

```
##Harvest numbers
Here I'm getting harvest numbers for apply the estimates to create stock specific harvest esimtate for each mixture and I created an [OceanAK](https://oceanak.dfg.alaska.local) report that pulls sockeye salmon harvest numbers for each fishing day and statisticl area in Cook Inlet.  The results of this report are saved in long format [here](2017 UCI commercial harvest report_5.8.18.csv) 
```{r get harvest numbers}

harvests<-read_csv("2017 UCI commercial harvest report_5.8.18.csv") %>% 
  select(year="Batch Year", month_day="Date Fishing Began (MM/DD)",gear_type="Gear Name",stat_area="Stat Area",stat_area_name="Stat Area Name",harvest="Number Of Animals (sum)") %>% 
  separate(month_day, c("day","month"), sep="-") %>% 
  mutate(month=sapply(month,function(mo){match(mo, month.abb)})) %>% 
  mutate(date=as.Date(paste(month, day , year, sep = "." ), format = "%m.%d.%Y"))

```

##Check sample dates for each capture_location
```{r}
bind_rows(lapply(mixvec,function(mix){
  
  get(paste0(mix,".gcl"))$attributes %>% 
    as.tibble() %>% 
    group_by(CAPTURE_LOCATION) %>% 
    summarize(min_date=min(CAPTURE_DATE),max_date=max(CAPTURE_DATE))
  
  }))

```


##Get sequences of represented harvest dates
These are the potential havest dates within 7 days of the first and last sample date to use when calculating represented harvest numbers. If there is more than one capture location for a mixture, use the latest start sample date and the earliest stop sample date for calculating min and max represented dates.  The actual represented harvest dates will be included in the harvest objects for each mixture.
```{r }

rep_dates<-sapply(mixvec,function(mix){
  
  dates=get(paste0(mix,".gcl"))$attributes %>% 
    as.tibble() %>% 
    group_by(CAPTURE_LOCATION) %>% 
    summarize(min_date=min(CAPTURE_DATE),max_date=max(CAPTURE_DATE));
  
  day=60*60*24;#seconds in a day
  
  week=7*day;#seconds in a week
  
  if(max(dates$min_date)-min(dates$min_date)>7){min_date=min(dates$min_date)}else{min_date=max(dates$min_date)-week_calc};
  
  if(max(dates$max_date)-min(dates$max_date)>7){max_date=max(dates$max_date)}else{max_date=min(dates$max_date)+week_calc};
  
  as.Date(seq(min_date,max_date,by=day))
  
})

bind_rows(lapply(rep_dates,FUN=range))#Range of represented dates

```

##Calculate harvest represented for each mixture
One thing to note about the stinking drift data is that there is a wonky stat code (24461), this is an error in the fish ticket database (fishermen put the wrong code in). Usually what we do is lump it in with the previous day’s 24460 harvest. (Email from Aaron Dupuis 1/11/2017)
```{r district-wide drift harvest}


Drift17_har <- harvests %>% filter(stat_area%in%c("24460","24461")&date%in%rep_dates$Drift17)%>% 
    summarise(rep_harvest=sum(harvest),ndays=length(unique(date)),start_date=min(date),end_date=max(date)) %>% 
     mutate(mix_collection="Drift17",total_harvest=sum(filter(harvests,gear_type=="Drift gillnet"&stat_area%in%c("24460","24461","24510"))$harvest))#Note: the number of days is 20, but actually it's 15 because of the 24461 stat area, Chinitna Bay (24510) is not represented by the mixture
  

Drift_Corridor17_har <- harvests %>% filter(gear_type=="Drift gillnet",stat_area%in%c("24456","24457")&date%in%rep_dates$Drift_Corridor17)%>% 
    summarise(rep_harvest=sum(harvest),ndays=length(unique(date)),start_date=min(date),end_date=max(date)) %>% 
     mutate(mix_collection="Drift_Corridor17",total_harvest=sum(filter(harvests,gear_type=="Drift gillnet"&stat_area%in%c("24456","24457"))$harvest))

West_Kalgin17_har <- harvests %>% filter(gear_type=="Set gillnet"&stat_area%in%c("24530","24550","24555","24560","24610","24620")&date%in%rep_dates$West_Kalgin17)%>% 
    summarise(rep_harvest=sum(harvest),ndays=length(unique(date)),start_date=min(date),end_date=max(date)) %>% 
     mutate(mix_collection="West_Kalgin17",total_harvest=sum(filter(harvests,gear_type=="Set gillnet"&stat_area%in%c("24510","24530","24550","24555","24560","24610","24620"))$harvest))

ESSN17_har <- harvests %>% filter(gear_type=="Set gillnet"&stat_area%in%c("24530","24550","24555","24560","24610","24620")&date%in%rep_dates$West_Kalgin17)%>% 
    summarise(rep_harvest=sum(harvest),ndays=length(unique(date)),start_date=min(date),end_date=max(date)) %>% 
     mutate(mix_collection="West_Kalgin17",total_harvest=sum(filter(harvests,gear_type=="Set gillnet"&stat_area%in%c("24510","24530","24550","24555","24560","24610","24620"))$harvest))




sort(unique(filter(harvests,gear_type=="Set gillnet")$stat_area))
```

